Brain Tumor Detection using Machine Learning Models

### 2021-08-03 slides.tex
slides completed

	\frame{\titlepage}

	\begin{frame}
		\frametitle{Overview}
		\tableofcontents
	\end{frame}

@@

		\begin{figure}[h]
			\centering
			\includegraphics[width=0.7\linewidth]{imgs/methodology}
			\caption{Proposed Methodology}%
			\label{fig:prop_methodology}
		\end{figure}

@@

		\begin{itemize}
			\item Binarization
			\item Filtering
			\item Edge Detection
			\item Segmentation
		\end{itemize}
	\end{frame}

@@

		\begin{center}
			\begin{tabular}{| c | c | c |}
				\hline
				Model & Implementation using TensorFlow & Implementation using
				fast.ai \\
				\hline
				CNN & 90.31\% & 92.66\% \\
				\hline
			\end{tabular}
		\end{center}
	\end{frame}
\end{document}

>>>>

	\begin{frame}
		\titlepage
	\end{frame}

	\begin{frame}
		\frametitle{Overview}
		\begin{columns}[totalwidth=0.9\textwidth]
			\hspace*{2.5cm}
			\begin{column}{0.35\textwidth}
				\tableofcontents[sections={1-4}]
			\end{column}
			\begin{column}{0.35\textwidth}
				\tableofcontents[sections={5-9}]
			\end{column}
		\end{columns}
	\end{frame}

@@

		\vspace{-1cm}

		\begin{figure}[h]
			\centering
			\includegraphics[width=\textwidth]{imgs/flowchart}
			\caption{Proposed Methodology}%
			\label{fig:prop_methodology}
		\end{figure}

@@

		\begin{itemize}
			\item Binarization
			\item Filtering
			\item Edge Detection
			\item Segmentation
		\end{itemize}

		\begin{block}{Segmentation}
			Image segmentation is the process of partitioning a digital image into multiple
			segments (sets of pixels, also known as image objects). The goal of
			segmentation is to simplify and/or change the representation of an image into
			something that is more meaningful and easier to analyze.
		\end{block}

@@

		\begin{table}
			\begin{center}
				\begin{tabular}{| c | c | c |}
					\hline
					Model & Implementation using TensorFlow & Implementation using
					fast.ai \\
					\hline
					CNN & 90.31\% & 92.66\% \\
					\hline
					VGG 15 & 97.38\% & 98.15\% \\
					\hline
					ResNet 50 & 97.54\% & 99.00\% \\
					\hline
				\end{tabular}
				\caption{Results in percent of the models implemented}
			\end{center}
	\end{table}
	\end{frame}

	\begin{frame}
		\frametitle{Results}
		\framesubtitle{CNN implemented using fast.ai and tensorflow}
		\begin{figure}[H]
			\centering
			\subfloat[cnn using tensorflow]
			{\includegraphics[width=0.4\linewidth]
			{imgs/tf_cnn.png}\label{tf_cnn_cmp}}
			\hspace{0.5cm}
			\subfloat[cnn using fast.ai]
			{\includegraphics[width=0.5\linewidth]
			{imgs/fastai_cnn.png}\label{fastai_vgg16_cmp}}
			\caption{CNN implemented in fast.ai and tensorflow}
			\label{CNN in fast.ai and tensorflow}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Results}
		\framesubtitle{VGG 16 implemented using fast.ai and tensorflow}
		\begin{figure}[H]
			\centering
			\subfloat[vgg16 using tensorflow]
			{\includegraphics[width=0.4\linewidth]
			{imgs/tf_vgg16.png}\label{tf_vgg16}}
			\hspace{0.5cm}
			\subfloat[vgg16 using fast.ai]
			{\includegraphics[width=0.5\linewidth]
			{imgs/fastai_vgg16.png}\label{fastai_vgg16}}
			\caption{VGG16 implemented in fast.ai and tensorflow}
			\label{VGG16 in fast.ai and tensorflow}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Results}
		\framesubtitle{ResNet 50 implemented using fast.ai and tensorflow}
		\begin{figure}[H]
			\centering
			\subfloat[resnet50 using tensorflow]
			{\includegraphics[width=0.4\linewidth]
			{imgs/tf_resnet.png}\label{tf_resnet}}
			\hspace{0.5cm}
			\subfloat[resnet50 using fast.ai]
			{\includegraphics[width=0.5\linewidth]
			{imgs/fastai_resnet.png}\label{fastai_resnet}}
			\caption{Resnet 50 implemented in fast.ai and tensorflow}
			\label{ResNet 50 in fast.ai and tensorflow}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Results}
		\framesubtitle{Predictions}

		\begin{figure}[H]
			\centering
			\subfloat[prediction made by VGG16 implemented in tensorflow]
			{\includegraphics[width=0.3\linewidth]
			{imgs/result.png}\label{vgg16_tf}}
			\hspace{0.3cm}
			\subfloat[prediction made by ResNet50 implemented in fast.ai]
			{\includegraphics[width=0.3\linewidth]
			{imgs/result_fast_ai.png}\label{resnet_fastai}}
			\caption{Comparing Predictions made by models}
			\label{fig:Results_Comparison}
		\end{figure}
	\end{frame}

	\section{Future Work}
	\begin{frame}
		\frametitle{Future Work}

		We further plan on implementing out experiments on other better machine
		learning model such as \textbf{GAN}

		A generative adversarial network (GAN) is a class of machine learning
		frameworks designed by Ian Goodfellow and his colleagues in 2014. Two
		neural networks contest with each other in a game (in the form of a
		zero-sum game, where one agent's gain is another agent's loss).

		We also plan on increasing out dataset for better training results.
	\end{frame}

	\begin{frame}
		\centering
		\textbf{\Huge Thank you}
	\end{frame}
\end{document}
